### 2012-12-07 doc/description.tex
addTables renamed to addTable

\documentclass[11pt]{article}
\usepackage{amssymb}
%\usepackage{semantic}

@@

\subsection{Application Structure evolution}
\subsubsection{Add Class}
\begin{verbatim}
op addClass : Class Application -> Application .
ceq addClass(C, A) = errApplication("inconsistent", A) 
   if containsName(classes(A), name(C))  
   or not referencesExist(associations(C), classes(A)) .
eq addClass(C, A) = application(classes(A) C, instances(A)) .
\end{verbatim}

@@

There is limitation connected with the implementation of platform. If there is a collection with the same name already existing table the evolution fails => rename a collection table

>>>>

\documentclass[11pt]{article}
\usepackage{amssymb}
\usepackage{semantic}

@@

\subsection{Application Structure Evolution}
The evolution of the application persistent layer is called refactoring. In this section we provide an overview of refactorings allowed in our ORM system.

\subsubsection{Add Class}
$
\inference[AddClass(C, A)=]{\forall c \in classes(A) : c.name != C.name}
{application(classes(A) \cup C, instances(A))}
$

\begin{verbatim}
op addClass : Class Application -> Application .
ceq addClass(C, A) = errApplication("inconsistent", A) 
   if containsName(classes(A), name(C))  
   or not referencesExist(associations(C), classes(A)) .
eq addClass(C, A) = application(classes(A) C, instances(A)) .
\end{verbatim}

@@

There is limitation connected with the implementation of platform. If there is a collection with the same name already existing table the evolution fails.
